\large \textbf{Leveraging Historical Ties between Cognitive Science and Computer Science to Guide Innovative Use of Computers in Education}

### 2016-02-03 paper.tex
Updates from ShareLaTeX

% sorting=none will order citations in order of appearance
% use sorting=nyt to sort by name, year, title
\usepackage[backend=biber,autolang=hyphen, bibencoding=inputenc, isbn=false, uniquename=false, sorting=none, sortcites=true, style=numeric, autocite=superscript, url=false]{biblatex} % biblatex setup
\DeclareLanguageMapping{american}{american-apa}
\appto{\bibfont}{\footnotesize} % for 10pt bibliography
%\usepackage{xunicode}
\usepackage[american]{babel}
\usepackage[babel]{csquotes}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage[dvipsnames,table]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows,shapes,fit}
\usepackage{standalone}
%\usepackage{mdframed}
\usepackage{changepage}
\usepackage{titlesec}
\usepackage[parfill]{parskip}

@@

\let\textcite=\autocite
\addbibresource{computing.bib}

@@

% conflict between teaching programming syntax, teaching ``how to program'', teaching high-level concepts like abstractions and how to ``do'' problem solving.
\section{Coding for Everyone}
In the past few years, there has been increasing interest to get more
people, regardless of background, to learn to program. In fact
President Obama recently made a statement calling on all children to
have the opportunity to learn about computer
science\autocite{whitehouse_computer_2016}. Sites such as code.org
promote CS education opportunities for all, citing statistics about
STEM jobs and arguing that in the 21st century knowledge about
computer science is foundational\autocite{code.org_every_2016}. Many
institutions of higher education either have programming requirements
for non-computer-science majors, or have been expanding programming to
non-majors\autocite{rich_cs1_2004,forte_motivation_2005,guzdial_design_2005}. At
the authors of this paper's institution, all first year general
engineering students are required to complete an introductory
programming module as part of their first-year engineering course.

@@

We needed a framework to consistently evaluate and starting from
\citeauthor{jamieson_creating_2009}'s
(\citeyear{jamieson_creating_2009}) to ground educational research
activities in how people learn we identified the concept of
\empha{constructive alignment} as a promising one. Following the
references in \citeauthor{jamieson_creating_2009}'s report as well as
conducting targeted literature searches for ``constructive alignment''
we were able to find descriptions of this
framework\autocite{jamieson_creating_2009,pellegrino_rethinking_2006,felder_designing_2003,biggs_enhancing_1996}.

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[babel]{csquotes}
\usepackage{graphicx}
\usepackage{etoolbox}
\usepackage{changepage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage[margin=1in]{geometry}

%\usepackage{xunicode}
\usepackage[dvipsnames,table]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows,shapes,fit}
\usepackage{standalone}

% sorting=none will order citations in order of appearance
% use sorting=nyt to sort by name, year, title
\usepackage[backend=biber,autolang=hyphen, bibencoding=inputenc, isbn=false, uniquename=false, sorting=none, sortcites=true, style=numeric, autocite=superscript, url=false]{biblatex} % biblatex setup
\addbibresource{./computing.bib}
\appto{\bibfont}{\footnotesize} % for 10pt bibliography

@@

\let\textcite=\autocite

@@

% conflict between teaching programming syntax, teaching ``how to program'', teaching high-level concepts like abstractions and how to ``do'' problem solving.
\section*{Coding for Everyone}
In the past few years, there has been increasing interest to get more
people, regardless of background, to learn to program. In fact
President Obama recently made a statement calling on all children to
have the opportunity to learn about computer
science\autocite{whitehouse_computer_2016}. Sites such as code.org
promote CS education opportunities for all, citing statistics about
STEM jobs and arguing that in the 21st century knowledge about
computer science is foundational\autocite{code.org_every_2016}. Many
institutions of higher education either have programming requirements
for non-computer-science majors, or have been expanding programming to
non-majors\autocite{rich_cs1_2004,forte_motivation_2005,guzdial_design_2005}. At
the authors of this paper's institution, all first year general
engineering students are required to complete an introductory
programming module as part of their first-year engineering course.

@@

We needed a framework to consistently evaluate and starting from
\citeauthor{jamieson_creating_2009}'s
(\citeyear{jamieson_creating_2009}) to ground educational research
activities in how people learn we identified the concept of
\emph{constructive alignment} as a promising one. Following the
references in \citeauthor{jamieson_creating_2009}'s report as well as
conducting targeted literature searches for ``constructive alignment''
we were able to find descriptions of this
framework\autocite{jamieson_creating_2009,pellegrino_rethinking_2006,felder_designing_2003,biggs_enhancing_1996}.
